A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2015-01-28 ms.tex
Re-word a few sentences in S5.1.3 and S7
from 0816602:
============

In ms.tex,

(*) Re-word a few sentences in S5.1.3 and S7

{\bf In typical radio interferometric measurements, due to the Fourier relation between sky brightness and measured visibilities, only short antenna spacings are sensitive to emission from large size scales such as the diffuse component in our study (angular scales $\gtrsim$~0.85\arcdeg). On the contrary, we note a very interesting signature of diffuse emission revealed at regions near the positive horizon delay limit in the {\it off--zenith} pointing, and at both horizon delay limits in the {\it zenith} pointing even on wide antenna spacings (125~m~$\lesssim |\boldsymbol{b}|\le$~200~m). This is a consequence of wide--field measurements, where long baselines are foreshortened due to projection effects towards off--axis emission, especially near the horizon. Consequently, they become sensitive to diffuse emission on large size scales. This holds for short baselines as well and is evident at all LSTs in our simulations}. Thus, diffuse emission from far off--axis directions manifests as an edge--heavy {\it two--pronged fork} across all baselines. It decreases in strength with increasing baseline length as expected but is present in all baseline orientations.

{\bf Interestingly, \citet{thy13} and \citet{pob13} have found a similar feature in their simulations and data respectively. In the latter, this feature is described as ``edge brightening'' and attributed to the Galactic plane near the horizon. From their discussion, it is unclear what fraction of power in that feature arises from ubiquitous diffuse emission. On the other hand, \citet{thy13} statistically modeled point sources below the confusion limit and attributed the feature to an increase in solid angles subtended by delay bins closer to the horizon limits thereby, enhancing the resulting integrated emission. This must be true for diffuse emission as well. Thus we argue the feature arises primarily due to an increase in sensitivity of long baselines to diffuse emission caused by foreshortening towards angles far off--axis. Consequently, the increased size scales (or solid angles) containing higher levels of integrated emission, and spatial scales inversely proportional to the foreshortened baseline lengths become matched}.

@@

{\bf Having examined the role foregrounds play in determining the delay power spectrum obtained with an interferometer array, we turn our attention to another crucial factor, namely, the power pattern of the antenna (refer to equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform}). In the following analysis, unlike the flagging of the edges of the coarse sub--bands described earlier in this paper, we assume an ideal flat passband over the entire 30.72~MHz bandwidth while still applying a {\it Blackman--Harris} window function. We also assume there are no random delay fluctuations in the MWA tile beamforming process}.

@@

{\bf In order to confirm that the {\it pitchfork} effect is independent of the specific foreground model chosen in our study, we also simulated the response to a uniformly illuminated sky. The brightness distribution on the sky was fixed to be a constant equal to the mean over the whole sky at 185~MHz with no spectral variation. This helps isolate the signatures of the antenna power pattern from those of the foregrounds.

@@

{\bf The delay power spectra for these antenna shapes are shown in Figure~\ref{fig:antennas-delay-spectra}. The occupancy of the power patterns in the sky hemisphere is clearly correlated with that in the delay spectra. Moreover, the following visual correlations are also apparent --- the strength of the primary lobe centered on the pointing center is correlated with the delay power spectrum centered on $\tau=0$; and, the overall rate of decrease in the power sensitivity away from the pointing center is correlated with the rate of drop in power away from $\tau=0$.

>>>>

{\bf In typical radio interferometric measurements, due to the Fourier relation between sky brightness and measured visibilities, only short antenna spacings are sensitive to emission from large size scales such as the diffuse component in our study (angular scales $\gtrsim$~0.85\arcdeg). However, we note a very interesting signature of diffuse emission revealed at regions near the positive horizon delay limit in the {\it off--zenith} pointing, and at both horizon delay limits in the {\it zenith} pointing even on wide antenna spacings (125~m~$\lesssim |\boldsymbol{b}|\le$~200~m). This is a consequence of wide--field measurements, where long baselines are foreshortened due to projection effects towards off--axis emission, especially near the horizon. Consequently, they become sensitive to diffuse emission on large size scales. This holds for short baselines as well and is evident at all LSTs in our simulations}. Thus, diffuse emission from far off--axis directions manifests as an edge--heavy {\it two--pronged fork} across all baselines. It decreases in strength with increasing baseline length as expected but is present in all baseline orientations.

{\bf \citet{thy13} and \citet{pob13} have found a similar feature in their simulations and data respectively. In the latter, this feature is described as ``edge brightening'' and attributed to the Galactic plane near the horizon. From their discussion, it is unclear what fraction of power in that feature arises from ubiquitous diffuse emission. On the other hand, \citet{thy13} statistically modeled point sources below the confusion limit and attributed the feature to an increase in solid angles subtended by delay bins closer to the horizon limits thereby, enhancing the resulting integrated emission. This must be true for diffuse emission as well. Thus we argue the feature arises primarily due to an increase in sensitivity of long baselines to diffuse emission caused by foreshortening towards angles far off--axis. Consequently, the increased size scales (or solid angles) containing higher levels of integrated emission, and spatial scales inversely proportional to the foreshortened baseline lengths become matched}.

@@

{\bf We now examine the influence of the antenna power pattern on the delay power spectrum (refer to equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform}). In the following analysis, we assume an ideal flat passband over the entire 30.72~MHz bandwidth while still applying a {\it Blackman--Harris} window function. We also assume there are no random delay fluctuations in the MWA tile beamforming process}.

@@

{\bf Simulations of the response to a uniformly illuminated sky confirm that the {\it pitchfork} effect is independent of the specific foreground model chosen in our study. The brightness distribution on the sky was fixed to be a constant equal to the mean over the whole sky at 185~MHz with no spectral variation. This helps isolate the signatures of the antenna power pattern from those of the foregrounds.

@@

{\bf The delay power spectra for these antenna shapes are shown in Figure~\ref{fig:antennas-delay-spectra}. The occupancy of the power patterns in the sky hemisphere is clearly correlated with that in the delay spectra. The following visual correlations are also apparent --- the strength of the primary lobe centered on the pointing center is correlated with the delay power spectrum centered on $\tau=0$; and, the overall rate of decrease in the power sensitivity away from the pointing center is correlated with the rate of drop in power away from $\tau=0$.
